---
title: "Rugby Results"
author: "Rishab Tirupathi"
date: "2023-10-31"
output: pdf_document
---
```{r setup, include=FALSE, warning=FALSE}
library(dplyr)
library(astsa)
library(tseries)
knitr::opts_chunk$set(echo = TRUE)
data = read.csv('results.csv')
```

## Create a table where we see the teams with the total points at home, away, the difference, and the average difference in points. 


```{r}
df = data |>
  filter(neutral == "False" & world_cup == 'False') |>
  arrange(date) |>
  group_by(home_team) |> 
  add_count(home_team)|>
  mutate(total_home = sum(home_score),
         total_away = sum(away_score),
         diff = total_home-total_away, 
         ave_diff = diff/n)|>
  select(c('home_team', 'total_home', 'total_away', 'diff', 'ave_diff')) |>
  distinct() |>
  arrange(-ave_diff, -diff, -total_home, -total_away)

rows = nrow(data |> filter(neutral == "False" & world_cup == 'False'))
df
print(sum(df$diff)/rows)
```

## Create a linear model to predict score difference

```{r}
mod_df = data |>
  filter(neutral == "False" & world_cup == 'False' & date >= '2015-01-01') |>
  arrange(date) |>
  mutate(diff = home_score-away_score) |>
  select(c('home_team', 'away_team', 'diff'))
mod = lm(diff ~ home_team + away_team, data = mod_df)
summary(mod)
```

We see that the intercept is positive, which indicates home team advantage. The model has a low R-squared so it could be improved. Each of the predictor variables is a binary variable - 1 if the team is playing 0 else. 
